### 2021-02-23 yfcc100m/paper/vldb2021/intro.tex
Update intro and design, minor changes in eval
Update intro/eval design, add more references

Despite the increasing use of visual data processing, 
there has been very little research on the \textit{management} of visual data.
Most of the current storage solutions for visual data are
an ad-hoc collection of tools and systems, that are re-purposed and 
adapted to work with visual data.
The approach of re-purposing and integrating solutions not designed for a task
results in resource utilization inefficiencies\cite{rasdaman}. 
For example, consider a ML developer constructing a pipeline
for extracting brain tumor information from existing brain images in a
classic medical imaging use case. 
This requires assigning consistent
identifiers for the scans and adding their metadata in
a relational or key-value database. 
If the queries require a search over patient information, 
then patients are associated with their brain scans. 
Finally, if the ML pipeline needs images with a different resolution than the original, there is additional compute
diverted towards pre-processing the original images which are typically larger. 
All these steps require understanding different software
solutions that provide various functionalities that can then be stitched
together with a script for this specific use case.
Moreover, if the pipeline identifies
new metadata to be added for the tumor images, most databases make it
hard to change the schema on the fly.
As another example, many applications can be studied through the use of large
and publicly available datasets. 
Applications include basic image search functionality (through the use
of human-generated tags), advanced image search through the use of
machine-generated tags and feature vectors\cite{imagesearch} 
for each image, and video summarization.
For these use-cases, the usual first step consists on selecting a 
subset of the data before running any processing, and a large effort 
is devoted to cleaning and pre-processing the data.
Selecting subsets of data is by itself a time consuming task,
as it involves loading all metadata into a solution that enables searching
based on tags (relational database, graph database, csv files, etc), and
building the necessary pipelines for querying and retrieving the right data.

More generally, data scientists and machine learning developers 
usually end up building an ad-hoc solution that results in a 
combination of databases and file systems to store 
metadata and visual data (images, videos), respectively. 
This is integrated with a set of custom scripts that tie multiple systems together, 
unique not only to a specific application/discipline but often 
to individual researchers or development teams.
These ad-hoc solutions make replicating experiments difficult, 
and more importantly, they do not scale well when deployed in the real-world.
The reason behind such complexity is \textit{the lack of a system 
that can be used to store and access all the data the application needs, 
including metadata, images, videos, and feature vectors}.

In this paper, we describe VDMS and show how it provides a 
comprehensive solution to the data management for applications 
that heavily rely on visual data. 
VDMS is a completely Open Source project designed to enable 
efficient access of visual data.
To the best of our knowledge, a rich set of functionalities 
designed for visual data management, provided behind an integrated API, 
is unique to VDMS and we were unable to find a system with similar functionality.
While there are a number of big-data frameworks~\cite{spark, hadoop}, systems
that can be used to store metadata~\cite{memsql, vertica}, and systems that
manipulate a specific category of visual data~\cite{scidb, rasdaman}, VDMS can
be distinguished from them on the following aspects:

>>>>

Despite the increasing use of visual data processing,
there has been very little research on the \textit{management} of visual data.
Most of the current storage solutions for visual data are
an ad-hoc collection of tools and systems, that are re-purposed and
adapted to work with visual data.
The approach of re-purposing and integrating solutions not designed for a task
results in resource utilization inefficiencies\cite{rasdaman}.
For example, consider a ML developer constructing a pipeline
for extracting brain tumor information from existing brain images in a
classic medical imaging use case.
This requires assigning consistent
identifiers for the scans and adding their metadata in
a relational or key-value database\cite{kumar2017data}.
If the queries require a search over patient information,
then patients are associated with their brain scans.
Finally, if the ML pipeline needs images with a different resolution
than the original, there is additional compute
diverted towards pre-processing the original images which are typically larger.
All these steps require understanding different software
solutions that provide various functionalities that can then be stitched
together with a script for this specific use case.
Moreover, if the pipeline identifies new metadata to be added for
the tumor images, most databases make it hard to change the schema on the fly.
As another example, many applications can be studied through the use of large
and publicly available datasets.
Applications include basic image search functionality (through the use
of human-generated tags), advanced image search through the use of
machine-generated tags and feature vectors\cite{imagesearch, qin2020similarity}
for each image, and video summarization.
For these use-cases, the usual first step consists on selecting a
subset of the data before running any processing, and a large effort
is devoted to cleaning and pre-processing the data.
Selecting subsets of data is by itself a time consuming task,
as it involves loading all metadata into a solution that enables searching
based on tags (relational database, graph database, csv files, etc), and
building the necessary pipelines for querying and retrieving the right data.

More generally, data scientists and machine learning developers
usually end up building an ad-hoc solution that results in a
combination of databases and file systems to store
metadata and visual data (images, videos), respectively \cite{sculley2015hidden}.
This is integrated with a set of custom scripts that tie multiple systems together,
unique not only to a specific application/discipline but often
to individual researchers or development teams
\cite{mayer2020scalable, sculley2015hidden}.
These ad-hoc solutions make replicating experiments difficult,
and more importantly, they do not scale well when deployed in the real-world.
The reason behind such complexity is \textit{the lack of a system
that can be used to store and access all the data the application needs,
including metadata, images, videos, and feature vectors}.

In this paper, we describe VDMS and show how it provides a
comprehensive solution to the data management for applications
that heavily rely on visual data.
VDMS is an Open Source project designed to enable
efficient access of visual data.
To the best of our knowledge, a rich set of functionalities
designed for visual data management, provided behind an integrated API,
is unique to VDMS and we were unable to find a system with similar functionality.
While there are a number of big-data frameworks~\cite{spark, hadoop}, systems
that can be used to store metadata~\cite{memsql, vertica, mysql, postgresql},
and systems that manipulate a specific category of
visual data~\cite{scidb, rasdaman},
VDMS can be distinguished from them on the following aspects:
